Syntax and Semantics of Abstract Binding Trees

### 2015-12-18 paper.tex
presheaf -> copresheaf; remove sheafification for now
we weren't using sheafification anywhere, so no point in defining it.

\paragraph{Presheaves on $\SCtx$}

@@

In the future, we will write $\SCtxSite$ for the Grothendieck site
$\Pair{\OpCat{\left(\SCtx\right)}}{J_\mathsf{atm}}$, where $J_\mathsf{atm}$ is
the atomic coverage. Sheafhood on the atomic site $\SCtxSite$ amounts to the
following condition, using Definition~\ref{def:support}:
\begin{quote}
  A presheaf $\Of{X}{\Sets^\SCtx}$ is a sheaf on $\SCtxSite$ just when, for all $\Member{n}{X(\Upsilon')}$, if we have
  \begin{tikzcd}[cramped]
    \IMode{\Upsilon}\arrow[r, hook, "\IMode{\varrho}"] & \IMode{\Upsilon'}
  \end{tikzcd}
  and $\Supports{\Upsilon}{\varrho}{n}$, then there is a unique
  $\Member{m}{X(\Upsilon)}$ such that $\IsEq{m\cdot\varrho}{n}$.
\end{quote}

Therefore, a sheaf on $\SCtxSite$ is a set that varies over $\Sorts$-sorted
symbols, which has a well-behaved notion of support. Another way to put it is,
if $\Member{m}{X(\Upsilon)}$ only ``uses'' some of the symbols available at
world $\Upsilon$, there's a canonical way to restrict $m$ to a term in the
world which contains \emph{only} the symbols that it uses.

\subsection{Constructions on sheaves}

For any Grothendieck site $\Match{\mathfrak{S}}{\Pair{\mathcal{C}}{J}}$, the
inclusion $\Of{\iota}{\Sheaves{\mathfrak{S}}\ra\Presheaves{\mathcal{C}}}$ of
sheaves into presheaves has a left adjoint
$\IMode{\Sheafify{(-)}}\dashv\IMode{\iota}$, which takes any presheaf
$\Of{X}{\Presheaves{\mathcal{C}}}$ to a unique sheaf
$\Of{\Sheafify{X}}{\Sheaves{\mathfrak{S}}}$, called the \emph{sheafification}
of $X$. Sheafification is the twice-iterated application of the
\emph{+-construction} $X^+$, which turns a presheaf into a separated presheaf,
and a separated presheaf into a sheaf \cite{mac-lane-moerdijk:1992}:
\begin{align*}
  \ADefine{
    X^+(C)
  }{
    \int^{S\in J(C)}
    \Hom{\Presheaves{\mathcal{C}}}{S}{X}
  }\\
  \ADefine{
    \Sheafify{X}
  }{
    X^{++}
  }
\end{align*}

We also have a canonical natural transformation $\Of{\eta}{X\ra X^+}$, defined
using the maximal sieve $\Define{t_C}{\Yoneda{C}}$:
\[
  \HypJ{
    \Define{\eta_C(m)}{
      \Pair{t_C}{
        X(-)(m)
      }
    }
  }{
    \Member{m}{X(C)}
  }
\]

>>>>

\paragraph{Copresheaves on $\SCtx$}

@@

In the future, we will write $\SCtxSite$ for the Grothendieck site
$\Pair{\OpCat{\left(\SCtx\right)}}{J_\mathsf{atm}}$, where $J_\mathsf{atm}$ is
the atomic coverage. Sheafhood on the atomic site $\SCtxSite$ amounts to the
following condition, using Definition~\ref{def:support}:
\begin{quote}
  A copresheaf $\Of{X}{\Sets^\SCtx}$ is a sheaf on $\SCtxSite$ just when, for all $\Member{n}{X(\Upsilon')}$, if we have
  \begin{tikzcd}[cramped]
    \IMode{\Upsilon}\arrow[r, hook, "\IMode{\varrho}"] & \IMode{\Upsilon'}
  \end{tikzcd}
  and $\Supports{\Upsilon}{\varrho}{n}$, then there is a unique
  $\Member{m}{X(\Upsilon)}$ such that $\IsEq{m\cdot\varrho}{n}$.
\end{quote}

Therefore, a sheaf on $\SCtxSite$ is a set that varies over $\Sorts$-sorted
symbol contexts, which has a well-behaved notion of support. Another way to put
it is, if $\Member{m}{X(\Upsilon)}$ only ``uses'' some of the symbols available
at world $\Upsilon$, there's a canonical way to restrict $m$ to a term in the
world which contains \emph{only} the symbols that it uses.

\paragraph{Constructions on sheaves}

%% For any Grothendieck site $\Match{\mathfrak{S}}{\Pair{\mathcal{C}}{J}}$, the
%% inclusion $\Of{\iota}{\Sheaves{\mathfrak{S}}\ra\Presheaves{\mathcal{C}}}$ of
%% sheaves into presheaves has a left adjoint
%% $\IMode{\Sheafify{(-)}}\dashv\IMode{\iota}$, which takes any presheaf
%% $\Of{X}{\Presheaves{\mathcal{C}}}$ to a unique sheaf
%% $\Of{\Sheafify{X}}{\Sheaves{\mathfrak{S}}}$, called the \emph{sheafification}
%% of $X$. Sheafification is the twice-iterated application of the
%% \emph{+-construction} $X^+$, which turns a presheaf into a separated presheaf,
%% and a separated presheaf into a sheaf \cite{mac-lane-moerdijk:1992}:
%% \begin{align*}
%%   \ADefine{
%%     X^+(C)
%%   }{
%%     \int^{S\in J(C)}
%%     \Hom{\Presheaves{\mathcal{C}}}{S}{X}
%%   }\\
%%   \ADefine{
%%     \Sheafify{X}
%%   }{
%%     X^{++}
%%   }
%% \end{align*}
%%
%% We also have a canonical natural transformation $\Of{\eta}{X\ra X^+}$, defined
%% using the maximal sieve $\Define{t_C}{\Yoneda{C}}$:
%% \[
%%   \HypJ{
%%     \Define{\eta_C(m)}{
%%       \Pair{t_C}{
%%         X(-)(m)
%%       }
%%     }
%%   }{
%%     \Member{m}{X(C)}
%%   }
%% \]
